% ============================================================
% Amazon-VT CFP 2026-2027 — AKG-E Full Proposal: Budget (DRAFT)
% Single-page LaTeX article
% DRAFT — dollar amounts are placeholders for PI/lab-admin review
% ============================================================

\documentclass[10pt]{article}
\usepackage[margin=0.75in]{geometry}
\usepackage{booktabs}
\usepackage{array}
\usepackage{microtype}
\pagestyle{empty}

\begin{document}

\begin{center}
{\large\bfseries Budget --- AKG-E Full Proposal (DRAFT)} \\[2pt]
\small\itshape (DRAFT --- for PI / lab-admin review; dollar amounts are placeholders)
\end{center}

\vspace{0.4em}

\noindent\textbf{Project:} Agentic Knowledge Graphs for AI-Accelerated Engineering with Simulation-Grounded Validation \\
\textbf{PI:} Kereshmeh Afsari \quad \textbf{Co-PI:} Chris Brown \quad \textbf{Student Researcher:} Jason Cusati \\
\textbf{Sponsor:} Amazon--Virginia Tech Initiative, CFP 2026--2027 \\
\textbf{Period:} 12 months (3-month aggressive build + 9-month dissemination / scaling)

\vspace{0.6em}

\begin{tabular}{p{4.4in} r}
  \toprule
  \textbf{Category}                                              & \textbf{Amount} \\
  \midrule
  \multicolumn{2}{l}{\textbf{Personnel}} \\
  \quad GRA \#1 --- Cusati (12 mo, full-time; primary student researcher)        & \$50,000 \\
  \quad\quad Stipend (12-mo full-time GRA)                                       & \$30,000 \\
  \quad\quad Tuition (annual VT graduate, sponsored-research rate)               & \$18,000 \\
  \quad\quad Benefits / fringe (\textasciitilde 7\% on stipend)                  & \$2,000 \\
  \quad GRA \#2 --- TBD (12 mo, \textasciitilde 25\% effort; engineering support) & \$14,000 \\
  \quad\quad Stipend (pro-rated)                                                 & \$8,000 \\
  \quad\quad Tuition (pro-rated)                                                 & \$5,000 \\
  \quad\quad Benefits / fringe                                                   & \$1,000 \\
  \quad Faculty summer salary --- Afsari, 1 mo (optional)                        & \$14,000 \\
  \midrule
  \multicolumn{2}{l}{\textbf{Materials and Computing}} \\
  \quad \textbf{LLM API tokens} (development + benchmark runs)                   & \$8,000 \\
  \quad AWS Bedrock + cloud compute (KG hosting, serving, scaling experiments)   & \$10,000 \\
  \quad Simulation software / FEA licenses (FEniCS open-source + utilities)      & \$1,000 \\
  \midrule
  \multicolumn{2}{l}{\textbf{Travel}} \\
  \quad Conference travel (AI-for-engineering / agentic AI venue)                & \$2,000 \\
  \quad Amazon collaboration travel (Seattle / Arlington)                        & \$1,000 \\
  \midrule
  \textbf{Total Direct Costs}                                                    & \$100,000 \\
  Indirect Costs (gift research --- no F\&A applied)                             & \$0 \\
  \midrule
  \textbf{Total Project Cost}                                                    & \textbf{\$100,000} \\
  \bottomrule
\end{tabular}

\vspace{1em}

\noindent\textbf{Justification --- LLM API Tokens.}
AKG-E is, by construction, a high-volume LLM workload: each iteration of the propose~$\to$~VVUQ~$\to$~feedback loop spends tokens on retrieval-augmented generation over the curated knowledge graph, on structured graph queries that surface code provisions and physical-law constraints, on simulation feedback ingestion (FEA / digital-twin / PDE solver outputs returned to the agent), and on the refinement step that consumes gate-emitted violations to produce the next candidate artifact. The benchmark evaluation amplifies this footprint substantially: three baselines (B0 Claude alone; B1 Claude~+~graph-RAG; B2 full AKG-E) are run across three engineering domains (construction, transportation, energy), with $n\geq5$ random seeds per cell and bootstrap resampling for 95\% confidence intervals on the headline correctness, calibration, and efficiency metrics. The full benchmark therefore drives thousands of multi-turn agent runs at production-quality model tokens, and the LLM API line is sized to support both day-to-day development and full benchmark execution without throttling. Separating this line from cloud compute prevents the token spend from being absorbed into a generic AWS line item where Amazon reviewers and VT lab admin cannot audit it independently.

\vspace{0.6em}

\noindent\textit{Notes for reviewers:} Total ask of \$100{,}000 matches the Amazon-VT CFP guidance (``\textasciitilde\$100K range, funded as gift research''). The award is gift research, so no F\&A indirect cost is applied; if Amazon elects to rescope as sponsored research, F\&A will be added at the VT-applicable rate and the personnel lines adjusted accordingly. Personnel allocation reflects that GRA~\#1 (Cusati) is the primary student researcher executing the build, with GRA~\#2 providing supplementary engineering bandwidth at \textasciitilde 25\% effort during peak build phases. Dollar amounts are draft estimates pending PI sign-off; final GRA stipend, tuition, and fringe rates for the 2026--2027 academic year are subject to VT lab-admin confirmation. The faculty summer salary line is optional and may be zeroed at the PI's discretion (reducing total to \$86{,}000, with the difference reallocatable to compute / LLM tokens if Amazon prefers a full \$100K ask).

\end{document}
